My Linux Notes

### 2018-07-21 Ubuntu_16.04_setup/mylinux.Rmd
up

Navigation
=====

@@

Network
=====

@@

Remote Control Via SSH
=====

>>>>

Common Techniques
========

## Copy Previous Command to file

```bash
cat ~/foo.txt >> doc.Rmd
echo "!!" >> file.txt
```

Then the command appends literal `cat ~/foo.txt >> doc.Rmd
echo "!!" >> file.txt` to the end of `file.txt`.

## Expansion with text

Download all web pages starting from `www.millionbook.net/wx/j/jingyong/sdxl/001.htm` to `www.millionbook.net/wx/j/jingyong/sdxl/041.htm`:

```bash
url=http://www.millionbook.net/wx/j/jingyong/sdxl/
wget "$url"{001..041}".htm"
```

Navigation
========

## File Manipulation

### Recursive Rename

Systematically rename multiple files by `for` loop.

Original files in the working dir:
```
dir2/
01-file.txt
02-file.txt
.
.
41-file.txt
README.md
```

```bash
for i in {01..41}
do 
	mv $(echo $i'*') $(echo $i'.txt')
done
```

After executing the code above:
```
dir2/
01.txt
02.txt
.
.
41.txt
README.md
```

@@

Network
========

@@

Remote Control Via SSH
========
